SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Adjust the position of the table in Sect.5.4 to reduce the blank in the middle of page 25.

\ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds. Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators. Such theories may be intrinsically undecidable, or may not  be properly handled by the SMT engine (e.g. for recursive datatypes).
However, while building the open automaton, which is a symbolic representation of the pNet behaviour, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT. So the open automaton may have more transitions and states than the theoretical minimum.}

@@

@@

        \medskip
        In the basic cases ($EnableState$, $EnableData$) there is no
        benefit, and even an overhead in the case of $EnableData$,
        because of the extra step of checking SAT at the end of the
        algorithm.
But as soon as there are more OTs in the system and not all
states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
the considered use-cases, with 50\% of time saving for the $FailureTimer$,
over to 80\% for the composition, depending
        on the nature of the examples, but increasing significantly
        with their complexity.

>>>>

\ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds. Also, the accuracy of a ``SAT'' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators. Such theories may be intrinsically undecidable, or may not  be properly handled by the SMT engine (e.g. for recursive datatypes).
However, while building the open automaton, which is a symbolic representation of the pNet behaviour, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT. So the open automaton may have more transitions and states than the theoretical minimum.}

@@

In the basic cases ($EnableState$, $EnableData$) there is no
benefit, and even an overhead in the case of $EnableData$,
because of the extra step of checking SAT at the end of the
algorithm.

But as soon as there are more OTs in the system and not all
states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
the considered use-cases, with 50\% of time saving for the $FailureTimer$,
over to 80\% for the composition, depending
on the nature of the examples, but increasing significantly
with their complexity.

@@

\medskip
